Spikes demo

### 2018-09-28 analysis/spikesdemo.Rmd
Working on summarize.gaussian.sims.R revisions for manuscript.

Simulate the noisy observations from the normal distribution with
means that are given by the "spikes" function, and with
spatially-structured variances.

>>>>

Simulate the noisy observations from the normal distribution with
means that are given by the "spikes" function, and with
spatially-structured variances given by the "clipped blocks" function.
